---
title: "Using rebib in general"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{04-GeneralUse}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup,echo = FALSE}
library(rebib)
```


While using rebib with a LaTeX document, one can use the following two options as per their needs :

## 1. Bibliography Converter
The bibliography converter will convert any LaTex or BBL file given as a path. This way, one can generate BibTeX from the embedded bibliography or BBL file.

```{r bibliocon, echo = TRUE}
wd <-  system.file("standalone", package = "rebib")
bbl_path <- paste(wd, "sample.bbl", sep = "/")
rebib::biblio_convertor(bbl_path)
```


## 2. Bibliography Aggregator
The bibliography aggregator will append the existing BibTeX file with bibliographic entries extracted from the LaTeX or BBL file.

The Flow Chart here visualizes the sequence.
```{r bib_agg,fig.alt="A Flow chart of Bibliography Aggregation",fig.align='center',fig.cap="A Flow chart of Bibliography Aggregation",echo=FALSE}
knitr::include_graphics("../man/figures/bib_agg.svg")
```

```{r biblioaggr, echo = FALSE}
wd <-  system.file("aggr_example", package = "rebib")
cat(readLines(paste(wd,"example.bib",sep="/")),sep = "\n")
# for files with BibTeX source as well as embedded entries
rebib::aggregate_bibliography(wd)
cat(readLines(paste(wd,"example.bib",sep="/")),sep = "\n")
```
