---
title: "Using rebib with RJarticle"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{use-with-rjarticle}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup,echo=FALSE}
library(rebib)
```

While using rebib with RJ article LaTeX files one can use the following two options as per their needs :

## 1. Bibliography Constructor

In bibliography construction mode, rebib will check for existing BibTeX files and will convert the embedded bibliography only when there are no 
linked BibTeX files in the RJ article.

``` latex
%% typically rebib will search for this line in the RJ article, not the RJwrapper file
\bibliography{example}
```
If there is no linked BibTeX file, rebib will begin its procedure of converting the embedded bibliography to BibTeX and then link it with the article file as well.

### Usage example

```{r rebibcons, echo=TRUE}
wd <-  system.file("article", package = "rebib")
bib_path <- paste0(wd,"/example.bib")
file.remove(bib_path)
# for files without BibTeX source
rebib::handle_bibliography(wd)
cat(readLines(paste(wd,"example.bib",sep="/")),sep = "\n")
```
## 2. Bibliography Aggregation
If you have a BibTeX file and it is missing some references then this mode can help you read the embedded bibliography and combine the two bibliographies in a single BibTeX file.

### Usage example

```{r rebibaggr, echo=TRUE}
wd <-  system.file("aggr_example", package = "rebib")
cat(readLines(paste(wd,"example.bib",sep="/")),sep = "\n")
# for files with BibTeX source as well as embedded entries
rebib::aggregate_bibliography(wd)
cat(readLines(paste(wd,"example.bib",sep="/")),sep = "\n")
```
